SunPy - Python for Solar Physics

### 2014-01-27 2-Data_Types.tex
First glob of edits

\section{Core Data Types}
The primary focus of the SunPy package is to provide data structures 
that are specifically designed for the various types of solar physics data, namely
images, time series, and spectra. SunPy provides three data core
objects to support these data types, 2D spatial data 
(\texttt{Map}), 1D temporal series (\texttt{LightCurve}) and 1 and 2D spectra 
(\texttt{Spectrum} and \texttt{Spectrogram}).

The philosophy of these objects is that they should provide a access to the original data
along with associated meta data and provide appropriate convenience functions to
enable data analysis and visualization. For all core data types, the data is stored in 
stored in the \texttt{.data}) attribute while the meta data is stored 
in the \texttt{.meta} attribute. It is 
possible to instantiate the data types from various different 
sources, \textit{e.g.} files, urls, arrays or time ranges.  In order to provide
instrument-specific specialisation, all the core SunPy data types support specialisation, 
\textit{i.e.} \texttt{Map} has an \texttt{AIAMap} sub-type. 
Data visualisation is provided by two functions; \texttt{peek()}, allows quick view plotting
, while more fine-grained control plotting that integrates with 
\texttt{matplotlib} is provided by \texttt{plot()}.

This section will give a brief overview of the \textit{current} functionality 
of each of these modules.

@@

\subsection{Visualisation}
\label{subsec:Viz}
As has been demonstrated in this section, the core SunPy datatypes 
include visualisation code that is specialised to that data type. 
These visualisation methods all currently utilise the matplotlib 
package, and are designed in such a way that they integrate well with 
the pyplot functional interface of matplotlib, as demonstrated in 
Figure \ref{code:mpl_1}.

@@

#Add a title
plt.title("My AIA plot")
plt.show()
\end{minted}
\end{minipage}
\caption{A simple example of how SunPy's plotting functions provide similar 
behaviour to matplotlib's pyplot interface.}
\label{code:mpl_1}
\end{listing}

This design philosophy makes the behaviour of SunPy's visualisation 
routines intuitive to those who already understand how matplotlib's 
interface is designed as well as allowing the use of the standard 
matplotlib commands to change the plot, \textit{e.g.} set the title. 
More technically what is done in the plotting routines is firstly, to 
make sure that the current state of the figure and axes is mantained 
in the same way as it is inside the \texttt{pyplot} functions. For 
\texttt{Map} this means setting \texttt{pyplot.sci()} or set current 
image, so that \texttt{plt.colorbar()} 
automatically detects the plotted \texttt{AxesImage} object. 
Secondly, it also means returning the same type of object as the 
\texttt{pyplot} interfaces function, \textit{i.e.} for \texttt{Map} 
it returns the \texttt{AxesImage} instance which is the same type of 
return as \texttt{pyplot.imshow}.

>>>>

\section{Core Data Types}
The primary focus of SunPy is to provide data structures 
that are specifically designed for the various kinds of solar physics data, namely
images, time series, and spectra. SunPy provides three core data
types using Python classes:
\texttt{Map} (2D spatial data),
\texttt{LightCurve} (1D temporal series)
and \texttt{Spectrum}/\texttt{Spectrogram} (1 and 2D spectra).

The classes provide access to the original data
along with associated metadata and provide appropriate convenience functions to
enable data analysis and visualization. For each of these classes, the data is
stored in the \texttt{.data} attribute while the metadata is stored 
in the \texttt{.meta} attribute. It is 
possible to instantiate the data types from various different 
sources: \textit{e.g.}, files, URLs, arrays or time ranges.  In order to provide
instrument-specific specialisation, all the core SunPy data types support specialisation;
\textit{e.g.}, \texttt{Map} has an \texttt{AIAMap} sub-type. 
Data visualisation is provided by two functions: \texttt{peek()}, for quick plotting,
and \texttt{plot()}, for more fine-grained control plotting that integrates with 
\texttt{matplotlib}.

This section will give a brief overview of the \textit{current} functionality 
of each of these data types.

@@

\subsection{Visualisation}
\label{subsec:Viz}
As has been demonstrated in this section, the core SunPy datatypes 
include visualisation code that is tailored to that data type. 
These visualisation methods all currently utilise the matplotlib 
package, and are designed in such a way that they integrate well with 
the \texttt{pyplot} functional interface of \texttt{matplotlib}, as demonstrated in 
Figure \ref{code:mpl_1}.

@@

#Add a title
plt.title("My AIA plot")
plt.show()
\end{minted}
\end{minipage}
\caption{A simple example of how SunPy's plotting functions provide similar 
behaviour to the \texttt{matplotlib.pyplot} interface.}
\label{code:mpl_1}
\end{listing}

This design philosophy makes the behaviour of SunPy's visualisation 
routines intuitive to those who already understand the \texttt{matplotlib}
interface, as well as allowing the use of the standard 
\texttt{matplotlib} commands to manipulate the plot parameters, such as the title.

%ayshih - I recommend removing the following sentences
More technically what is done in the plotting routines is firstly, to 
make sure that the current state of the figure and axes is maintained 
in the same way as it is inside the \texttt{pyplot} functions. For 
\texttt{Map} this means setting \texttt{pyplot.sci()} or set current 
image, so that \texttt{plt.colorbar()} 
automatically detects the plotted \texttt{AxesImage} object. 
Secondly, it also means returning the same type of object as the 
\texttt{pyplot} interfaces function, \textit{i.e.} for \texttt{Map} 
it returns the \texttt{AxesImage} instance which is the same type of 
return as \texttt{pyplot.imshow}.

### 2014-01-27 3-3-HELIO.tex
First glob of edits

Obtain from all the catalogues these which name contain our event of interest
>>> catalogues = hc.get_table_names()
>>> catalogues_event = [l[0] for l in catalogues if event_type in l[0]]
>>> print catalogues_event
['hi_cme_list', 'cactus_stereoa_cme', 'icme_earth_cycle23', 'cactus_cme_list', '
goes_flare_no_sep_radio_cme', 'ulysses_swoops_icme', 'cme_forbush_event', 'seeds
_cme', 'cme_inner_heliosphere', 'mars_earth_icme', 'stereo_hi_cme', 'cactus_ster
eob_cme', 'cactus_soho_cme', 'lasco_cme_list', 'cactus_stb_cme_list', 'cactus_so
ho_cme_list', 'halo_cme_flare_magnetic_storm', 'lasco_cme_cat', 'cactus_sta_cme_
list', 'stereoa_impactplastic_icme', 'stereob_impactplastic_icme', 'soho_lasco_c
me', 'stereo_impactplastic_icme', 'wind_typeii_soho_cme']

Query all the catalogues that comes from cactus
>>> results = [hc.time_query(tstart, tend, event) 
...            for event in catalogues_event if 'cactus' in event]
>>> print results
********** This need to be added!
\end{minted}
\caption{Example of querying the HEC service.}
\label{code:helio}
\end{listing}

>>>>

#Obtain from all the catalogues these which name contain our event of interest
>>> catalogues = hc.get_table_names()
>>> catalogues_event = [l[0] for l in catalogues if event_type in l[0]]

#Query all the catalogues that comes from cactus
>>> results = [hc.time_query(tstart, tend, event) 
...            for event in catalogues_event if 'cactus' in event]
>>> print results
********** This need to be added!
\end{minted}
\caption{Example of querying the HEC service.}
\label{code:helio}
\end{listing}
